Identifying Effective Motivational Interviewing Sequences Using Automated Pattern Analysis

### 2018-05-28 jhir/latex-manuscript/manuscript.tex
update figure 1

\date{Received: 3 December 2017 /Revised: 16 April 2018, 29 June 2018 /Accepted: }
% The correct dates will be entered by the editor

@@

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{figures/bic-vs-hidden-states.eps}
\caption{Bayesian information criterion (BIC) of HMM models of successful (left) and unsuccessful (right) interviews by varying the number of hidden states}
\label{fig:bic}
\end{figure*}

>>>>

\date{Received: 3 December 2017 /Revised: 16 April 2018 and 29 June 2018 /Accepted: }
% The correct dates will be entered by the editor

@@

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{figures/bic-vs-hidden-states.eps}
\caption{\hl{Bayesian information criterion (BIC) of HMM models of successful (left) and unsuccessful (right) interviews by varying the number of hidden states}}
\label{fig:bic}
\end{figure*}
